---
title: 'Analyses Study 2'
author: 
output: 
  github_document:
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(rmarkdown)
```

# Scripts


# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
```

# Analyses

```{r "data for analyses"}
load(here("data/intermediate/s2.RData"))
dw <-d %>% 
  drop_na(weight)
dw <- svydesign(id=~1, weights=~weight, data=dw)
```

Next, we automatically extract a `.md` file for the online appendix, as well as a  latex table for the manuscript. 
We are using jinja2 template [src/analysis/table_descriptives.tex.j2](table.tex.j2) which is called with a json string containing the data.
To replicate, make sure `env/bin/pip install -U j2cli` is installed via your command line.

```{r "Table with Descriptives"}
source(here("src/analysis/descr-overview-s2.R"))

kbl(descr, booktabs =T, caption = "Descriptives") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")   

rm(descr)
```

## H2: The political left is more likely to endorse conspiracy theories involving economic elites, while the political right is more likely to endorse conspiracy theories involving political and cultural elites
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/s2.R"))

p1

(p2a +p2b)/(p2c + p2d) +
  plot_layout(guides = 'collect') &
  theme(legend.position = 'bottom',
        legend.direction = 'vertical')

tl1 <- twolines(cb ~ ideology + gender + age + education, data = df)
tl2 <- twolines(cbs ~ ideology + gender + age + education, data = df)
tl3 <- twolines(cl ~ ideology + gender + age + education, data = df)
tl4 <- twolines(cr ~ ideology + gender + age + education, data = df)

(p3a +p3b)/(p3c + p3d) 
```

